Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
ijcai

\begin{abstract}
Several approaches have been proposed to improve automated software fault
diagnosis, aiming to reduce the effort and costs spent in debugging. This
paper reports the outcome of a study
performed to dismistify\Rui{We need to say something on why we
decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
suspect that several highly suspiscious components --- often involved in failing, 
but seldom in passed executions ---
may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
the failing tests source files that comprise the highest scored faulty
statements from the Defects4j dataset\Rui{not clear why this is in here for
the reader: Mozilla, minimizing test cases, ... }. The impact of Tandem-FL is evaluated
through computing the SFL score \Rui{SFL score: a reader does not know what that is}
of each fault before and after minimization\Rui{minimization: unknown to the
reader... He thinks that the study is on slicing}.
This study also discusses on limitations of dynamic slicing, such as the potential
of missing faulty statements. Our
results show that combining SFL with dynamic slicing improves the diagnostic
accuracy in \Rui{x\% on average}, hence leading to the root cause of observed failures faster.
\end{abstract}

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
\label{tab:df4j}
\end{table}
\normalsize

>>>>

\begin{abstract}
Several approaches have been proposed to improve automated software fault
diagnosis, aiming to reduce the effort and costs spent in debugging. 
Dynamic Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are very popular techniques and normally seen as complementary. However, this combination has not been entirely explored yet.
Thus, this paper reports the outcome of an empirical study
performed to demystify the impact of combining \ds{} with \sfl{}, a technique we coin as Tandem-FL. 
We
suspect that several highly suspicious components --- often involved in failing, 
but seldom in passed executions ---
may be unrelated to the bug. 
This study also discusses on limitations of dynamic slicing, such as the potential
of missing faulty statements. Our
results show that combining SFL with dynamic slicing improves the diagnostic
accuracy in \Rui{x\% on average}, hence leading to the root cause of observed failures faster.
\end{abstract}

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (LOC)$^{*}$ & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            &   & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           &   & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         &   & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           &   & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           &   & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         &   & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}

\label{tab:df4j}
\end{table}
\normalsize
